---
title: "2018 11 7"
output: html_notebook
---


```{r}
library(readr)
collegeData <- read_csv("https://quality.data.gov.tw/dq_download_csv.php?nid=6231&md5_url=dda8fca407131483c1d8cbf3d61cf793")
```
```{r}
library(dplyr)
mutate(collegeData,
       `日間∕進修別`=as.factor(`日間∕進修別`),
       等級別=as.factor(等級別),
       一年級男生=as.numeric(一年級男生),
       一年級女生=as.numeric(一年級女生)
      ) ->
 collegeData2

collegeData %>%
  mutate(.,"日間/進修別"=as.factor("日間/進修別"),
          等級別=as.factor(等級別),
          一年級男生=as.numeric(一年級男生),
          一年級女生=as.numeric(一年級女生),
           )->collegeData2
```
```{r}
library(dplyr)
collegeData %>%
mutate(
       `日間∕進修別`=as.factor(`日間∕進修別`),
       等級別=as.factor(等級別),
       一年級男生=as.numeric(一年級男生),
       一年級女生=as.numeric(一年級女生)
       ) ->
  collegeData2
```
```{r}
library(dplyr)
library(readr)
cl<-locale(grouping_mark = ",") 
collegeData2 %>% 
  mutate(
    `日間∕進修別`=as.factor(`日間∕進修別`),
    等級別=as.factor(等級別),
    一年級男生=parse_number(一年級男生,locale=cl),
    一年級女生=parse_number(一年級女生,locale=cl)
  ) -> collegeData4
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
